Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications

### 2025-12-09 Submission.tex
r.version output removed
final edits

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics\newline\indent Word count: 4,942}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications},
  pdfauthor={Alicia Stachowski2, John Kulas1, \& Renata García Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={O*NET, challenge-hindrance framework, job demands-resources, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). Our primary aims explore: 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association (of subjective appraisals) with positive and negative outcomes, and 3) the buffering effect of resources on the relationships between demands and negative work outcomes\footnote{Took out previous \#2 -- make sure this isn't revisited in Results or Discussion}. We investigate these associations via the lens of \href{https://www.onetcenter.org/content.html}{O*NET job specifications}, which provide a near--exhaustive listing of generalizable characteristic specifications.

\hypertarget{theoretical-foundations}{%
\subsection{Theoretical Foundations}\label{theoretical-foundations}}

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007). Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout. Bakker et al. (2005) explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, Xanthopoulou et al. (2007) also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows (see Figure \ref{fig:ourmodel}):

@@

\begin{verbatim}
##                _                                
## platform       x86_64-w64-mingw32               
## arch           x86_64                           
## os             mingw32                          
## crt            ucrt                             
## system         x86_64, mingw32                  
## status                                          
## major          4                                
## minor          3.1                              
## year           2023                             
## month          06                               
## day            16                               
## svn rev        84548                            
## language       R                                
## version.string R version 4.3.1 (2023-06-16 ucrt)
## nickname       Beagle Scouts
\end{verbatim}

\hypertarget{method}{%
\section{Method}\label{method}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

@@

\hypertarget{materials}{%
\subsection{Materials}\label{materials}}

\hypertarget{characteristics-challenge-demands-hindrance-demands-and-resources}{%
\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}}

@@

\hypertarget{stress}{%
\subsubsection{Stress}\label{stress}}

@@

\hypertarget{outcome-associations}{%
\subsubsection{Outcome Associations}\label{outcome-associations}}

@@

Table 2 presents empirical associations between estimates of resource, challenge, and hindrance and worker \emph{engagement}, \emph{stress}, and \emph{burnout}. Here, workers' perceptions were aggregated across all characteristics to provide indications of ``overall'' resource and demand experience. Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate. The more percieved hindrances, the higher the rating of stress, indicating only weak partial support for Hypothesis 3b. All subsequent analyses retain this ``overall'' operationalization of workers' experience of resources, challenges, and hindrances.

\hypertarget{challenges-resources-and-job-outcomes}{%
\subsubsection{Challenges, Resources, and Job Outcomes}\label{challenges-resources-and-job-outcomes}}

@@

Regarding Hypothesis 4a, challenge demands and resources did not explain a significant amount of the variance in stress, \(R^2\) = 0.01, Adj. \(R^2\) = 0, \(F(2, 565) = 1.67\), \(p = .189\). The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.17, and thus does not support the presence of moderation. These challenge demands and resources did, however, explain a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj. \(R^2\) = 0.04, \(F(2, 565) = 1.67\), \(p = .189\). The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 2.25, and thus collectively these analyses fail to provide statistical support for the presence of moderation (Hypothesis 4a). In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge demands and the outcomes of strain and burnout.

@@

\hypertarget{hindrances-resources-and-job-outcomes}{%
\subsubsection{Hindrances, Resources, and Job Outcomes}\label{hindrances-resources-and-job-outcomes}}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) some characteristics were more likely to vary across demand and resource, 3) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes. We found that job characteristics were not uniquely categorized as a resource or demand, but rather, job characteristics were often viewed similarly as both a resource and a challenging demand. The findings broadly revealed further that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in hindering elements across workers and jobs. While engagement exhibits moderate associations with all investigated perceptions, we did not find support for the prediction that different types of demands would be related to stress and burnout, but we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).

@@

\hypertarget{limitations-and-future-directions}{%
\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}}

As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring. First, although we aggregated to O*NET groupings, we were also dealing with single-item measures for much our operationalization. Although not ideal psychometrically, this provided a strong linkage to the established O*NET framework. Related to that, we intentionally worked within the O*NET database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources and demands. Therefore, to the extent that O*NET is not an exhaustive repository, there are existing characteristics that we did not capture. For example, O*NET also includes styles and values, which we did not sample. Future studies may want to expand to explore these additional aspects of work.

Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example \ref{fig:combinegraphs2}), perhaps reflecting some artificiality (for example, indicating ``not terribly hindering'' if the physical demand was not commonplace).

We also retained the literature-derived definitions of resources, challenges, and hindrances (Demerouti et al., 2001). Given the high associations observed between ratings of resource and challenge, it is possible that respondents did not distinguish between these definitions as cleanly as we intended. Future investigations may wish to explore the colloquial versus academic phrasing of these questions and how that may impact observed associations between resources and challenges. We also note that effect sizes were small and thus it is important to consider the practical significance when thinking about potential interventions. We encourage future thought on how consideration of resource and demand perceptions might be combined with moderators to reduce employee stress and burnout, as well as enhance engagement.

@@

\hypertarget{references}{%
\section{References}\label{references}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-abbas2019challenge}{}}%
Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2014job}{}}%
Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2017job}{}}%
Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2005job}{}}%
Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2007job}{}}%
Bakker, A. B., Hakanen, J. J., Demerouti, E., \& Xanthopoulou, D. (2007). Job resources boost work engagement, particularly when job demands are high. \emph{Journal of Educational Psychology}, \emph{99}(2), 274.

\leavevmode\vadjust pre{\hypertarget{ref-bakker2013weekly}{}}%
Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.

\leavevmode\vadjust pre{\hypertarget{ref-burr2019third}{}}%
Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T. S., Llorens, C., Navarro, A., et al. (2019). The third version of the copenhagen psychosocial questionnaire. \emph{Safety and Health at Work}, \emph{10}(4), 482--503.

\leavevmode\vadjust pre{\hypertarget{ref-campbell1959convergent}{}}%
Campbell, D. T., \& Fiske, D. W. (1959). Convergent and discriminant validation by the multitrait-multimethod matrix. \emph{Psychological Bulletin}, \emph{56}(2), 81--105.

\leavevmode\vadjust pre{\hypertarget{ref-cavanaugh2000empirical}{}}%
Cavanaugh, M. A., Boswell, W. R., Roehling, M. V., \& Boudreau, J. W. (2000). An empirical examination of self-reported work stress among US managers. \emph{Journal of Applied Psychology}, \emph{85}(1), 65.

\leavevmode\vadjust pre{\hypertarget{ref-chen2021daily}{}}%
Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.

\leavevmode\vadjust pre{\hypertarget{ref-crawford2010linking}{}}%
Crawford, E. R., LePine, J. A., \& Rich, B. L. (2010). Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. \emph{Journal of Applied Psychology}, \emph{95}(5), 834.

\leavevmode\vadjust pre{\hypertarget{ref-cronbach1951coefficient}{}}%
Cronbach, L. J. (1951). Coefficient alpha and the internal structure of tests. \emph{Psychometrika}, \emph{16}(3), 297--334.

\leavevmode\vadjust pre{\hypertarget{ref-demerouti2001job}{}}%
Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.

\leavevmode\vadjust pre{\hypertarget{ref-gerich2017relevance}{}}%
Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.

\leavevmode\vadjust pre{\hypertarget{ref-hakanen2008job}{}}%
Hakanen, J. J., Schaufeli, W. B., \& Ahola, K. (2008). The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement. \emph{Work \& Stress}, \emph{22}(3), 224--241.

\leavevmode\vadjust pre{\hypertarget{ref-horan2020review}{}}%
Horan, K. A., Nakahara, W. H., DiStaso, M. J., \& Jex, S. M. (2020). A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research. \emph{Frontiers in Psychology}, \emph{11}, 560346.

\leavevmode\vadjust pre{\hypertarget{ref-kim2020thriving}{}}%
Kim, M., \& Beehr, T. A. (2020). Thriving on demand: Challenging work results in employee flourishing through appraisals and resources. \emph{International Journal of Stress Management}, \emph{27}(2), 111.

\leavevmode\vadjust pre{\hypertarget{ref-kubicek2023all}{}}%
Kubicek, B., Uhlig, L., Hülsheger, U. R., Korunka, C., \& Prem, R. (2023). Are all challenge stressors beneficial for learning? A meta-analytical assessment of differential effects of workload and cognitive demands. \emph{Work \& Stress}, \emph{37}(3), 269--298.

\leavevmode\vadjust pre{\hypertarget{ref-lazarus1984stress}{}}%
Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.

\leavevmode\vadjust pre{\hypertarget{ref-lepine2005meta}{}}%
LePine, J. A., Podsakoff, N. P., \& LePine, M. A. (2005). A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance. \emph{Academy of Management Journal}, \emph{48}(5), 764--775.

\leavevmode\vadjust pre{\hypertarget{ref-lepine2022challenge}{}}%
LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.

\leavevmode\vadjust pre{\hypertarget{ref-peterson2001understanding}{}}%
Peterson, N. G., Mumford, M. D., Borman, W. C., Jeanneret, P. R., Fleishman, E. A., Levin, K. Y., Campion, M. A., Mayfield, M. S., Morgeson, F. P., Pearlman, K., et al. (2001). Understanding work using the occupational information network (o* NET): Implications for practice and research. \emph{Personnel Psychology}, \emph{54}(2), 451--492.

\leavevmode\vadjust pre{\hypertarget{ref-pindek2024dynamic}{}}%
Pindek, S., Meyer, K., Valvo, A., \& Arvan, M. (2024). A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies. \emph{Journal of Business and Psychology}, 1--19.

\leavevmode\vadjust pre{\hypertarget{ref-podsakoff2007differential}{}}%
Podsakoff, N. P., LePine, J. A., \& LePine, M. A. (2007). Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis. \emph{Journal of Applied Psychology}, \emph{92}(2), 438.

\leavevmode\vadjust pre{\hypertarget{ref-rosen2020challenges}{}}%
Rosen, C. C., Dimotakis, N., Cole, M. S., Taylor, S. G., Simon, L. S., Smith, T. A., \& Reina, C. S. (2020). When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes. \emph{Journal of Applied Psychology}, \emph{105}(10), 1181.

\leavevmode\vadjust pre{\hypertarget{ref-schaufeli2017applying}{}}%
Schaufeli, W. B. (2017). Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational Dynamics}, \emph{46}(2), 120--132.

\leavevmode\vadjust pre{\hypertarget{ref-searle2015merits}{}}%
Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.

\leavevmode\vadjust pre{\hypertarget{ref-webster2010toward}{}}%
Webster, J. R., Beehr, T. A., \& Christiansen, N. D. (2010). Toward a better understanding of the effects of hindrance and challenge stressors on work behavior. \emph{Journal of Vocational Behavior}, \emph{76}(1), 68--77.

\leavevmode\vadjust pre{\hypertarget{ref-webster2011extending}{}}%
Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

\leavevmode\vadjust pre{\hypertarget{ref-xanthopoulou2007job}{}}%
Xanthopoulou, D., Bakker, A. B., Dollard, M. F., Demerouti, E., Schaufeli, W. B., Taris, T. W., \& Schreurs, P. J. (2007). When do job demands particularly predict burnout? The moderating role of job resources. \emph{Journal of Managerial Psychology}, \emph{22}(8), 766--786.

\leavevmode\vadjust pre{\hypertarget{ref-R-careless}{}}%
Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\makeatother
\keywords{O*NET, challenge-hindrance framework, job demands-resources, job characteristics}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Shared Characterizations of Challenging Demands and Job Resources across O*NET Element Classifications},
  pdfauthor={Alicia Stachowski2, John Kulas1, \& Renata García Prieto Palacios Roji3},
  pdflang={en-EN},
  pdfkeywords={O*NET, challenge-hindrance framework, job demands-resources, job characteristics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on a growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). Our primary aims explore: 1) variability in subjective ratings of job characteristics with respect to perception as resource and/or demand, 2) differential association (of subjective appraisals) with positive and negative outcomes, and 3) the buffering effect of resources on the relationships between demands and negative work outcomes. We investigate these associations via the lens of \href{https://www.onetcenter.org/content.html}{O*NET job specifications}, which provide a near--exhaustive listing of generalizable characteristic specifications.

\subsection{Theoretical Foundations}\label{theoretical-foundations}

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007). Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout. Bakker et al. (2005) explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, Xanthopoulou et al. (2007) also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttressed the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows (see Figure \ref{fig:ourmodel}):

@@

\begin{verbatim}
##                _                                
## platform       x86_64-w64-mingw32               
## arch           x86_64                           
## os             mingw32                          
## crt            ucrt                             
## system         x86_64, mingw32                  
## status                                          
## major          4                                
## minor          5.0                              
## year           2025                             
## month          04                               
## day            11                               
## svn rev        88135                            
## language       R                                
## version.string R version 4.5.0 (2025-04-11 ucrt)
## nickname       How About a Twenty-Six
\end{verbatim}

\section{Method}\label{method}

\subsection{Participants}\label{participants}

@@

\subsection{Materials}\label{materials}

\subsubsection{Characteristics, Challenge Demands, Hindrance Demands, and Resources}\label{characteristics-challenge-demands-hindrance-demands-and-resources}

@@

\subsubsection{Stress}\label{stress}

@@

\subsubsection{Outcome Associations}\label{outcome-associations}

@@

Table 2 presents empirical associations between estimates of resource, challenge, and hindrance and worker \emph{engagement}, \emph{stress}, and \emph{burnout}. Here, workers' perceptions were aggregated across all characteristics to provide indications of ``overall'' resource and demand experience. Engagement exhibited non-trivial associations with all three types of perception whereas stress was only associated with the hindrance aggregate. The more percieved hindrances, the higher the rating of stress (\(r\)=.11, \(p\)\textless.01), indicating only weak partial support for Hypothesis 3b. All subsequent analyses retain this ``overall'' operationalization of workers' experience of resources, challenges, and hindrances.

\subsubsection{Challenges, Resources, and Job Outcomes}\label{challenges-resources-and-job-outcomes}

@@

Regarding Hypothesis 4a, challenge demands and resources did not explain a significant amount of the variance in stress, \(R^2\) = 0.01, Adj. \(R^2\) = 0.00, \(F(2, 565) = 1.67\), \(p = .189\). The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 0.17, and thus does not support the presence of moderation. These challenge demands and resources did, however, explain a statistically significant amount of the variability in burnout, \(R^2\) = 0.04, Adj. \(R^2\) = 0.04, \(F(2, 565) = 1.67\), \(p = .189\). The inclusion of the interaction term in step two of the model did not contribute a significant addition to the model, \(F(3, 564) = 1.17\), \(p = .320\), \(\Delta R^2\) = 0.00, \(\Delta F\) (1, 564) = 2.25, and thus collectively these analyses fail to provide statistical support for the presence of moderation (Hypothesis 4a). In sum, these findings do not provide support for the assertion that resources would moderate the relationships between challenge demands and the outcomes of strain and burnout.

@@

\subsubsection{Hindrances, Resources, and Job Outcomes}\label{hindrances-resources-and-job-outcomes}

@@

\section{Discussion}\label{discussion}

The major aims of this paper were to explore whether: 1) there was variability in subjective ratings of job characteristics as resources and demands, 2) subjective appraisals were differentially related to positive and negative outcomes, and lastly, 3) if resources buffer the relationships between demands (challenge and hindrance) and outcomes. We found that job characteristics were not uniquely categorized as a resource or demand, but rather, job characteristics were often viewed similarly as both a resource and a challenging demand. The findings broadly revealed further that there was relatively more consistency in ratings of resource and challenge characteristics, and far more variability in hindering elements across workers and jobs. While engagement exhibits moderate associations with all investigated perceptions, we did not find support for the prediction that different types of demands would be related to stress and burnout, but we did find that resources moderated the challenge-engagement relationship, and further, resources moderated the hindrance-stress, and hindrance-burnout relationships (as predicted).

@@

\subsection{Limitations and Future Directions}\label{limitations-and-future-directions}

As with all individual studies, this project was limited in scope, and as such, there are a number of avenues for future study worth exploring. First, although we aggregated to O*NET groupings, we were also dealing with single-item measures for much our operationalization. Although not ideal psychometrically, this provided a strong linkage to the established O*NET framework. Related to that, we intentionally worked within the O*NET database, and in selecting job context and activity items, did not include other types of job characteristics that may be important resources and demands. Therefore, to the extent that O*NET is not an exhaustive repository, there are existing characteristics that were not captured. Future studies may want to expand to explore additional aspects of work.

Hindrances exhibit greater variability, but a visual scan of the items reveals some with heavy physicality content (see, for example Figure \ref{fig:combinegraphs2}), perhaps reflecting some artificiality (for example, indicating ``not terribly hindering'' if the physical demand was not commonplace).

We also retained the literature-derived definitions of resources, challenges, and hindrances (Demerouti et al., 2001). Given the high associations observed between ratings of resource and challenge, it is possible that respondents did not distinguish between these definitions as cleanly as we intended. Future investigations may wish to explore the colloquial versus academic phrasing of characteristics and how that may impact observed associations between resources and challenges. We also note that effect sizes were small and thus it is important to consider the practical significance when thinking about potential interventions. We encourage future thought on how consideration of resource and demand perceptions might be combined with moderators to reduce employee stress and burnout, as well as enhance engagement.

@@

\newpage

\section{References}\label{references}

@@

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-abbas2019challenge}
Abbas, M., \& Raja, U. (2019). Challenge-hindrance stressors and job outcomes: The moderating role of conscientiousness. \emph{Journal of Business and Psychology}, \emph{34}(2), 189--201.

\bibitem[\citeproctext]{ref-bakker2014job}
Bakker, A. B., \& Demerouti, E. (2014). Job demands--resources theory. \emph{Wellbeing: A Complete Reference Guide}, 1--28.

\bibitem[\citeproctext]{ref-bakker2017job}
Bakker, A. B., \& Demerouti, E. (2017). Job demands--resources theory: Taking stock and looking forward. \emph{Journal of Occupational Health Psychology}, \emph{22}(3), 273.

\bibitem[\citeproctext]{ref-bakker2005job}
Bakker, A. B., Demerouti, E., \& Euwema, M. C. (2005). Job resources buffer the impact of job demands on burnout. \emph{Journal of Occupational Health Psychology}, \emph{10}(2), 170.

\bibitem[\citeproctext]{ref-bakker2007job}
Bakker, A. B., Hakanen, J. J., Demerouti, E., \& Xanthopoulou, D. (2007). Job resources boost work engagement, particularly when job demands are high. \emph{Journal of Educational Psychology}, \emph{99}(2), 274.

\bibitem[\citeproctext]{ref-bakker2013weekly}
Bakker, A. B., \& Sanz-Vergel, A. I. (2013). Weekly work engagement and flourishing: The role of hindrance and challenge job demands. \emph{Journal of Vocational Behavior}, \emph{83}(3), 397--409.

\bibitem[\citeproctext]{ref-burr2019third}
Burr, H., Berthelsen, H., Moncada, S., Nübling, M., Dupret, E., Demiral, Y., Oudyk, J., Kristensen, T. S., Llorens, C., Navarro, A., et al. (2019). The third version of the copenhagen psychosocial questionnaire. \emph{Safety and Health at Work}, \emph{10}(4), 482--503.

\bibitem[\citeproctext]{ref-campbell1959convergent}
Campbell, D. T., \& Fiske, D. W. (1959). Convergent and discriminant validation by the multitrait-multimethod matrix. \emph{Psychological Bulletin}, \emph{56}(2), 81--105.

\bibitem[\citeproctext]{ref-cavanaugh2000empirical}
Cavanaugh, M. A., Boswell, W. R., Roehling, M. V., \& Boudreau, J. W. (2000). An empirical examination of self-reported work stress among US managers. \emph{Journal of Applied Psychology}, \emph{85}(1), 65.

\bibitem[\citeproctext]{ref-chen2021daily}
Chen, H., Wang, H., Yuan, M., \& Xu, S. (2021). Daily challenge/hindrance demands and cognitive wellbeing: A multilevel moderated mediation model. \emph{Frontiers in Psychology}, \emph{12}, 616002.

\bibitem[\citeproctext]{ref-crawford2010linking}
Crawford, E. R., LePine, J. A., \& Rich, B. L. (2010). Linking job demands and resources to employee engagement and burnout: A theoretical extension and meta-analytic test. \emph{Journal of Applied Psychology}, \emph{95}(5), 834.

\bibitem[\citeproctext]{ref-cronbach1951coefficient}
Cronbach, L. J. (1951). Coefficient alpha and the internal structure of tests. \emph{Psychometrika}, \emph{16}(3), 297--334.

\bibitem[\citeproctext]{ref-demerouti2001job}
Demerouti, E., Bakker, A. B., Nachreiner, F., \& Schaufeli, W. B. (2001). The job demands-resources model of burnout. \emph{Journal of Applied Psychology}, \emph{86}(3), 499.

\bibitem[\citeproctext]{ref-gerich2017relevance}
Gerich, J. (2017). The relevance of challenge and hindrance appraisals of working conditions for employees' health. \emph{International Journal of Stress Management}, \emph{24}(3), 270.

\bibitem[\citeproctext]{ref-hakanen2008job}
Hakanen, J. J., Schaufeli, W. B., \& Ahola, K. (2008). The job demands-resources model: A three-year cross-lagged study of burnout, depression, commitment, and work engagement. \emph{Work \& Stress}, \emph{22}(3), 224--241.

\bibitem[\citeproctext]{ref-horan2020review}
Horan, K. A., Nakahara, W. H., DiStaso, M. J., \& Jex, S. M. (2020). A review of the challenge-hindrance stress model: Recent advances, expanded paradigms, and recommendations for future research. \emph{Frontiers in Psychology}, \emph{11}, 560346.

\bibitem[\citeproctext]{ref-kim2020thriving}
Kim, M., \& Beehr, T. A. (2020). Thriving on demand: Challenging work results in employee flourishing through appraisals and resources. \emph{International Journal of Stress Management}, \emph{27}(2), 111.

\bibitem[\citeproctext]{ref-kubicek2023all}
Kubicek, B., Uhlig, L., Hülsheger, U. R., Korunka, C., \& Prem, R. (2023). Are all challenge stressors beneficial for learning? A meta-analytical assessment of differential effects of workload and cognitive demands. \emph{Work \& Stress}, \emph{37}(3), 269--298.

\bibitem[\citeproctext]{ref-lazarus1984stress}
Lazarus, R. S., \& Folkman, S. (1984). \emph{Stress, appraisal, and coping}. Springer publishing company.

\bibitem[\citeproctext]{ref-lepine2005meta}
LePine, J. A., Podsakoff, N. P., \& LePine, M. A. (2005). A meta-analytic test of the challenge stressor--hindrance stressor framework: An explanation for inconsistent relationships among stressors and performance. \emph{Academy of Management Journal}, \emph{48}(5), 764--775.

\bibitem[\citeproctext]{ref-lepine2022challenge}
LePine, M. A. (2022). The challenge-hindrance stressor framework: An integrative conceptual review and path forward. \emph{Group \& Organization Management}, \emph{47}(2), 223--254.

\bibitem[\citeproctext]{ref-peterson2001understanding}
Peterson, N. G., Mumford, M. D., Borman, W. C., Jeanneret, P. R., Fleishman, E. A., Levin, K. Y., Campion, M. A., Mayfield, M. S., Morgeson, F. P., Pearlman, K., et al. (2001). Understanding work using the occupational information network (o* NET): Implications for practice and research. \emph{Personnel Psychology}, \emph{54}(2), 451--492.

\bibitem[\citeproctext]{ref-pindek2024dynamic}
Pindek, S., Meyer, K., Valvo, A., \& Arvan, M. (2024). A dynamic view of the challenge-hindrance stressor framework: A meta-analysis of daily diary studies. \emph{Journal of Business and Psychology}, 1--19.

\bibitem[\citeproctext]{ref-podsakoff2007differential}
Podsakoff, N. P., LePine, J. A., \& LePine, M. A. (2007). Differential challenge stressor-hindrance stressor relationships with job attitudes, turnover intentions, turnover, and withdrawal behavior: A meta-analysis. \emph{Journal of Applied Psychology}, \emph{92}(2), 438.

\bibitem[\citeproctext]{ref-rosen2020challenges}
Rosen, C. C., Dimotakis, N., Cole, M. S., Taylor, S. G., Simon, L. S., Smith, T. A., \& Reina, C. S. (2020). When challenges hinder: An investigation of when and how challenge stressors impact employee outcomes. \emph{Journal of Applied Psychology}, \emph{105}(10), 1181.

\bibitem[\citeproctext]{ref-schaufeli2017applying}
Schaufeli, W. B. (2017). Applying the job demands-resources model: A `how to'guide to measuring and tackling work engagement and burnout. \emph{Organizational Dynamics}, \emph{46}(2), 120--132.

\bibitem[\citeproctext]{ref-searle2015merits}
Searle, B. J., \& Auton, J. C. (2015). The merits of measuring challenge and hindrance appraisals. \emph{Anxiety, Stress, \& Coping}, \emph{28}(2), 121--143.

\bibitem[\citeproctext]{ref-webster2010toward}
Webster, J. R., Beehr, T. A., \& Christiansen, N. D. (2010). Toward a better understanding of the effects of hindrance and challenge stressors on work behavior. \emph{Journal of Vocational Behavior}, \emph{76}(1), 68--77.

\bibitem[\citeproctext]{ref-webster2011extending}
Webster, J. R., Beehr, T. A., \& Love, K. (2011). Extending the challenge-hindrance model of occupational stress: The role of appraisal. \emph{Journal of Vocational Behavior}, \emph{79}(2), 505--516.

\bibitem[\citeproctext]{ref-xanthopoulou2007job}
Xanthopoulou, D., Bakker, A. B., Dollard, M. F., Demerouti, E., Schaufeli, W. B., Taris, T. W., \& Schreurs, P. J. (2007). When do job demands particularly predict burnout? The moderating role of job resources. \emph{Journal of Managerial Psychology}, \emph{22}(8), 766--786.

\bibitem[\citeproctext]{ref-R-careless}
Yentes, R. D., \& Wilhelm, F. (2021). \emph{Careless: Procedures for computing indices of careless responding}.
